{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-28 main.tex
Jonathan commit
Changes to introduction, adding to BibTex, adding fda_gasoline example

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Function Data Analysis (FDA) is a relatively new field which is getting more attention as researchers from different fields collect more data from an continuous underlying process. This data still can be processed by classical statistical methods, but only FDA allows to answer questions that are tied to the information given by the smoothness of the underlying continuous process. (see \cite{levitin_introduction_2007})\\
	 As Kokoszka and Reimherr (2017) describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (see \cite[S.~17]{kokoszka_introduction_2017}.
	 To motivate the use of scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an continuous underlying process. In economics, on application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (see~\cite{Das_2019}).
